Make_mash_U_hyp

### 2020-07-09 R/Make_mash_U_hyp.Rmd
Test smaller Uhyp matrices for midwest and gulf subpops

gulf_loc <- c("CLMB", "KBSM", "KING", "PKLE", "TMPL")
midw_loc <- c("CLMB", "KBSM", "PKLE")
atl_loc <- c("CLMB", "KBSM", "LINC", "PKLE", "TMPL")
midwgulf_loc <- c("BRKG", "CLMB", "KBSM", "KING", "LINC", "PKLE", "STIL",
                  "TMPL")
U_gulf <- read_rds(file.path(path, "U_hyp_gulf_symmetric.rds"))
i = 2
  m_out <- mash_standard_run(path = path, numSNPs = numSNPs[i], U_hyp = U_gulf,
                             suffix = phe_suffix[i],
                             saveoutput = TRUE)
```

@@

i = 2
for(i in seq_along(mash_rds)){
  m <- readRDS(file.path(path, mash_rds[i]))
  suffix <- mash_suffix[i]
  p1 <- mash_plot_manhattan_by_condition(m, saveoutput = TRUE, suffix = suffix)
  p2 <- mash_plot_sig_by_condition(m, saveoutput = TRUE, suffix = suffix)
  p3 <- mash_plot_pairwise_sharing(m, saveoutput = TRUE, suffix = suffix)
  p4 <- mash_plot_effects(m, n = 1, saveoutput = TRUE, suffix = suffix)
  p5 <- mash_plot_effects(m, n = 2, saveoutput = TRUE, suffix = suffix)
  p6 <- mash_plot_covar(m, saveoutput = TRUE, suffix = suffix)
  p7 <- mash_plot_Ulist(m, range = get_U_by_mass(m), saveoutput = TRUE, 
                  suffix = suffix)
}
```

>>>>

gulf_loc <- c("CLMB", "KBSM", "KING", "PKLE", "TMPL")
midw_loc <- c("CLMB", "KBSM", "PKLE")
atl_loc <- c("CLMB", "KBSM", "LINC", "PKLE", "TMPL")
midwgulf_loc <- c("BRKG", "CLMB", "KBSM", "KING", "LINC", "PKLE", "STIL",
                  "TMPL")
U_gulf <- read_rds(file.path(path, "U_hyp_gulf.rds"))
i = 2
U_ed <- file.path(path, "Mash_data_driven_covariances_10000_gulf.rds")
  m_out <- mash_standard_run(path = path, numSNPs = numSNPs[i], U_ed = U_ed,
                             U_hyp = U_gulf, suffix = phe_suffix[i],
                             saveoutput = TRUE)
```

@@

i = 2
for(i in seq_along(mash_rds)){
  m <- readRDS(file.path(path, mash_rds[i]))
  suffix <- mash_suffix[i]
  p1 <- mash_plot_manhattan_by_condition(m, saveoutput = TRUE, suffix = suffix)
  p2 <- mash_plot_sig_by_condition(m, saveoutput = TRUE, suffix = suffix)
  p3 <- mash_plot_pairwise_sharing(m, saveoutput = TRUE, suffix = suffix)
  p4 <- mash_plot_effects(m, n = 1, saveoutput = TRUE, suffix = suffix)
  p5 <- mash_plot_effects(m, n = 2, saveoutput = TRUE, suffix = suffix)
  p6 <- mash_plot_covar(m, saveoutput = TRUE, suffix = suffix)
  p7 <- mash_plot_Ulist(m, range = get_U_by_mass(m), saveoutput = TRUE, 
                  suffix = suffix)
}
load_all("~/Github/switchgrassGWAS")
```

# Test mash with U_hyp

I got lots of errors the first time I ran mash to completion with U_hyp, and I am not yet certain why. I'd like to run mash on just FL50 in the gulf, and GDD in the midwest maybe, to see if I can diagnose what's going on or what the covariance matrices should look like.

## Rerun bigsnp2mashr

```{r}
trim_name <- function(x){
    for(i in seq_along(x)){
  if((str_sub(x[i], start = -1) %in% c("_")))
  { x[i] <- str_sub(x[i], end = -2) }
    }
  return(x)
}

pathin <- file.path("~", "Github", "pvdiv-phenology-gxe", "analysis", 
                       "gwas", "GDD")
path <- file.path("~", "Github", "pvdiv-phenology-gxe", "analysis", 
                       "gwas", "GDD", "Uhyp")

inputfiles <- read_delim(file.path("~", "Github", "pvdiv-phenology-gxe", 
                                   "analysis", "gwas", "inputkinship.txt"), 
                         delim = " ", col_names = "SNPfiles") 
# Midwest & Gulf, Midwest, Gulf, Atlantic, Midwest & Atlantic, Gulf & Atlantic

# Midwest
snp <- snp_attach(inputfiles$SNPfiles[2])
gwas_rds <- pvdiv_results_in_folder(path = pathin, 
                                    pattern = paste0("GWAS_datatable_",
                                                     "(KBSM|PKLE|CLMB)", ".+",
                                                     "(CGDD_12C)", 
                                                     ".+",
                                                     "\\d+g_8.8M"))

site_phe <- trim_name(str_sub(gwas_rds, start = 16, end = -41))
numSNPs <- 20000 #ceiling((1000000 / length(site_phe)^2)/1000)*1000

midwest_mashin <- 
  pvdiv_bigsnp2mashr(path = pathin, snp = snp,
                    gwas_rds = gwas_rds, phenotypes = site_phe, 
                    numSNPs = numSNPs, scale = FALSE, 
                    suffix = "midwest_uhyp1", saveoutput = TRUE)
# Gulf [3]
snp <- snp_attach(inputfiles$SNPfiles[3])
gwas_rds <- pvdiv_results_in_folder(path = pathin, 
                                    pattern = paste0("GWAS_datatable_", ".+",
                                                     "(FL50)", 
                                                     ".+",
                                                     "\\d+g_10.3M"))

site_phe <- trim_name(str_sub(gwas_rds, start = 16, end = -42))
numSNPs <- 30000 #ceiling((1000000 / length(site_phe)^2)/1000)*1000

gulf_mashin <- 
  pvdiv_bigsnp2mashr(path = pathin, snp = snp,
                    gwas_rds = gwas_rds, phenotypes = site_phe, 
                    numSNPs = numSNPs, scale = FALSE, suffix = "gulf_uhyp1", 
                    saveoutput = TRUE)
```

# Uhyp for midwest and gulf

```{r}
gulf_loc <- c("CLMB", "KBSM", "KING", "PKLE", "TMPL")
midw_loc <- c("CLMB", "KBSM", "PKLE")

Ugulfhyp <- list()
Umidwhyp <- list()

for(i in seq_along(names(Ureturn))){
  Ugulf1 <- Ureturn[[i]][which(rownames(Ureturn[[i]]) %in% gulf_loc),
                 which(colnames(Ureturn[[i]]) %in% gulf_loc)]
  Umidw1 <- Ureturn[[i]][which(rownames(Ureturn[[i]]) %in% midw_loc),
                 which(colnames(Ureturn[[i]]) %in% midw_loc)]

  Ugulfhyp <- list.append(Ugulfhyp, Ugulf1 = Ugulf1)
  Umidwhyp <- list.append(Umidwhyp, Umidw1 = Umidw1)
  names(Ugulfhyp)[i] <- names(Ureturn)[i]
  names(Umidwhyp)[i] <- names(Ureturn)[i]
}
str(Umidwhyp)
write_rds(Ugulfhyp, path = file.path(path, "U_hyp_gulf_1phe.rds"))
write_rds(Umidwhyp, path = file.path(path, "U_hyp_midw_1phe.rds"))
```

```{r}
path <- file.path("~", "Github", "pvdiv-phenology-gxe", "analysis", 
                       "gwas", "GDD", "Uhyp")
numSNPs <- 20000
suffix = "midwest_uhyp1"
Umidwhyp <- read_rds(path = file.path(path, "U_hyp_midw_1phe.rds"))

m <- mash_standard_run(path = path, numSNPs = numSNPs, U_hyp = Umidwhyp, 
                       suffix = suffix, saveoutput = TRUE)
```
